LOINC2HPO_EPIC AND SCC

### 2022-03-17 src/main/r/MSDW_HPO_Phenotype_Analysis.Rmd
update analysis

  return (df)
}
```

@@

tested_patient_count_by_year <- get_tested_patient_count_by_year()
```

@@

phenotype_rank_all_by_year <- get_phenotype_rank_all_by_year()
```

```{r}
plot_phenotypes_of_interest_by_year <- function(terms_of_interest, df, normalize=TRUE){
  hpo_terms_selected <- df %>% filter(termid %in% terms_of_interest) %>% select(termid, label) %>% distinct()

  y_str = ifelse(normalize, 'n_patient/n_tested', 'n_patient')
  y_label = ifelse(normalize, 'patient fraction among tested', 'patient count')

  p <- df %>% filter(termid %in% terms_of_interest) %>% 
    filter(lab_year <= 2019 & lab_year > 2000) %>%
    ggplot(aes(x = lab_year, y = eval(parse(text=y_str)), group = termid, color = termid)) + 
    geom_point() +
    geom_line() +
    scale_color_discrete(breaks = hpo_terms_selected$termid, labels = str_c(hpo_terms_selected$termid, hpo_terms_selected$label, sep = " ")) +
    ylab(y_label)

@@

hpo_level_1_terms <- phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=phenotype_rank_all_by_year, normalize = FALSE)
```

```{r}
hpo_level_1_terms <- phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df= phenotype_rank_all_by_year %>% left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'), normalize = TRUE)
```

@@

tested_phenotype_rank_direct <- get_tested_phenotype_rank_direct()
tested_phenotype_rank_all <- get_tested_phenotype_rank_all()
```

@@

For both cases, it would be interesting to learn about the changes of the lab phenotypes over time, and among different races.

@@

tested_phenotype_rank_direct_by_race <- get_tested_phenotype_rank_direct_by_race()
tested_phenotype_rank_all_by_race <- get_tested_phenotype_rank_all_by_race()
```

For each directly measured phenotype, we can determine whether race and the tests are correlated by some form of Chi-squared teste.
```{r}
tested_phenotype_rank_direct_by_race %>% filter(race == 'African American') %>% arrange(-n_record) %>% head(10) %>% formattable::formattable()
tested_phenotype_rank_direct_by_race %>% filter(race == 'Asian') %>% arrange(-n_record) %>% head(10) %>% formattable::formattable()
tested_phenotype_rank_direct_by_race %>% filter(race == 'White') %>% arrange(-n_record) %>% head(10) %>% formattable::formattable()
```

```{r}
tested_phenotype_rank_all_by_race %>% filter(race == 'African American' & distancetoroot == 1) %>% arrange(-n_record) %>% head(10) %>% formattable::formattable()
tested_phenotype_rank_all_by_race %>% filter(race == 'Asian' & distancetoroot == 1) %>% arrange(-n_record) %>% head(10) %>% formattable::formattable()
tested_phenotype_rank_all_by_race %>% filter(race == 'White' & distancetoroot == 1) %>% arrange(-n_record) %>% head(10) %>% formattable::formattable()
```

tested_phenotype_rank_all_by_year <- get_tested_phenotype_rank_all_by_year()
```

```{r}
hpo_level_1_terms <- tested_phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=tested_phenotype_rank_all_by_year, normalize = FALSE)
```
```{r}
plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=tested_phenotype_rank_all_by_year %>% left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'), normalize = TRUE)
```

```{r}
children_abnormal_cellular_physiology <- c('HP:0003220', 'HP:0011018', 'HP:0025463', 'HP:0011019', 'HP:0003254', 'HP:4000056', 'HP:0011133', 'HP:0004371', 'HP:0031377', 'HP:0031409', 'HP:0012103', 'HP:0032576', 'HP:0003204', 'HP:0004356', 'HP:0032571', 'HP:0002916', 'HP:0003224', 'HP:0003575', 'HP:0003358')
plot_phenotypes_of_interest_by_year(terms_of_interest = children_abnormal_cellular_physiology, df=tested_phenotype_rank_all_by_year)
```

Again, the above plot shows that it is driven by one HP:0031409 Abnormal lymphocyte physiology. 
```{r}
children_of_interest <- c('HP:0011840', 'HP:0030886', 'HP:0012177', 'HP:0005372', 'HP:0031378')
plot_phenotypes_of_interest_by_year(terms_of_interest = children_of_interest, df=tested_phenotype_rank_all_by_year)
```
```{r}
children_of_interest <- c('HP:0002847', 'HP:0002959', 'HP:0005384', 'HP:0041076', 'HP:0010701')
plot_phenotypes_of_interest_by_year(terms_of_interest = children_of_interest, df=tested_phenotype_rank_all_by_year)
```

```{r}
children_of_interest <- c('HP:0010702', 'HP:0032336', 'HP:0410241', 'HP:0410240', 'HP:0410243', 'HP:0410242', 'HP:0410244', 'HP:0004313')
plot_phenotypes_of_interest_by_year(terms_of_interest = children_of_interest, df=tested_phenotype_rank_all_by_year)
```

tested_phenotype_spike_by_loinc_year <- get_tested_phenotype_spike_by_loinc_year()
tested_phenotype_spike_by_localcode_year <- get_tested_phenotype_spike_by_localcode_year()
```

>>>>

FORCE_RERUN <- FALSE
```

@@

tested_patient_count_by_year <- get_tested_patient_count_by_year(force_rerun=FORCE_RERUN)
```

Collect tested patients by year, race and sex.

```{r}
get_tested_patient_count_by_year_race_sex <- function(force_rerun=FALSE, cache_dir=CACHE_DIR){
  df_path = glue('{cache_dir}/tested_patient_count_by_year_race_sex.csv')

  if (force_rerun | !file.exists(df_path)){
    df <- dbGetQuery(dsca, "
            with scc_lab as (
            	select medical_record_number , calendar_date as lab_date, date_part('Year', lab_date) as lab_year
            	from hai_az_prod.lab_scc_2020july lsj
            ), 
            epic_lab as (
            	select mrn as medical_record_number, order_date as lab_date, date_part('Year', lab_date) as lab_year
            	from hai_az_test.lab_epic_2020july lej
            ),
            scc_and_epic as (
            	select * 
            	from scc_lab 
            	union all
            	select * 
            	from epic_lab
            ),
            scc_and_epic_with_race as (
            	select lab.*, p.race, p.gender
            	from scc_and_epic lab
            	join hai_az_prod.person_msdw_2020july p using (medical_record_number)
            )
            select lab_year, race, gender, count(distinct medical_record_number) as n_patient
            from scc_and_epic_with_race
            group by lab_year, race, gender
            order by lab_year, race, gender;
            ")

tested_patient_count_by_year_race_sex <- get_tested_patient_count_by_year_race_sex(force_rerun=FORCE_RERUN)
```

@@

phenotype_rank_all_by_year <- get_phenotype_rank_all_by_year(force_rerun = FORCE_RERUN)

get_phenotype_rank_all_by_year_race_sex <- function(force_rerun=FALSE, cache_dir=CACHE_DIR){
  df_path = glue('{cache_dir}/observed_phenotype_rank_all_by_year_race_sex.csv')

  if (force_rerun | !file.exists(df_path)){
    df <- dbGetQuery(dsca, "
      with abnormal_lab as 
      	(select * 
      	from hai_az_prod.scc_and_epic_lab_after_loinc2hpo_2020july lab 
      	where hpotermid is not null and not isnegated
      	),
      abnormal_lab_after_infer as 
      	(SELECT l.medical_record_number, l.lab_date, date_part(year, lab_date) as lab_year, l.local_test_code, l.loinc, l.hpotermid, l.isnegated, pair.ancestor , pair.distance
      	FROM abnormal_lab l 
      	left join hai_az_prod.hpo_is_a_pairs pair on l.hpotermid = pair.current),
      lab_freq_by_year_race_sex as (
      	select ancestor as termid, lab_year, p.race, p.gender, count(*) as n_record, count(distinct medical_record_number) as n_patient 
      	from abnormal_lab_after_infer 
      	join hai_az_prod.person_msdw_2020july p using (medical_record_number)
      	group by ancestor, lab_year, p.race, p.gender
      )
      select *
      from lab_freq_by_year_race_sex
      join hai_az_prod.hpo h using (termid)
      order by lab_year, distancetoroot;")

phenotype_rank_all_by_year_race_sex <- get_phenotype_rank_all_by_year_race_sex(force_rerun = FORCE_RERUN)
```

```{r}
fancy_scientific <- function(l) {
     # turn in to character string in scientific notation
     l <- format(l, scientific = TRUE)
     # quote the part before the exponent to keep all the digits
     l <- gsub("^(.*)e", "'\\1'e", l)
     # turn the 'e+' into plotmath format
     l <- gsub("e", "%*%10^", l)
     # return this as an expression
     parse(text=l)
}

plot_phenotypes_of_interest_by_year <- function(terms_of_interest, df, normalize=TRUE){
  hpo_terms_selected <- df %>% filter(termid %in% terms_of_interest) %>% select(termid, label) %>% distinct()

  y_str = ifelse(normalize, 'n_patient/n_tested', 'n_patient')
  y_label = ifelse(normalize, 'patient fraction normalized to database size', 'patient count')

  p <- df %>% filter(termid %in% terms_of_interest) %>% 
    filter(lab_year <= 2019 & lab_year > 2000) %>%
    ggplot(aes(x = lab_year, y = eval(parse(text=y_str)), group = termid, color = termid)) + 
    geom_point() +
    geom_line() +
    scale_color_discrete(breaks = hpo_terms_selected$termid, labels = str_c(hpo_terms_selected$termid, hpo_terms_selected$label, sep = " ")) +
    xlab('Year') +
    ylab(y_label) +
    theme_bw() +
    theme(panel.grid = element_blank(),
        axis.title = element_text(size = 8), axis.text = element_text(size = 8), 
        legend.text = element_text(size = 8), legend.title = element_text(size = 10))

@@

hpo_level_1_terms <- phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=phenotype_rank_all_by_year, normalize = FALSE)
ggsave(filename = glue('{CACHE_DIR}/plot_abnormal_phenotypes_by_year_level_1.pdf'), plot = p, width = 8, height = 4)
p
```

```{r}
hpo_level_1_terms <- phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df= phenotype_rank_all_by_year %>%
                                           left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'), normalize = TRUE)
ggsave(filename = glue('{CACHE_DIR}/plot_abnormal_phenotypes_by_year_level_1_normalized.pdf'), plot = p, width = 8, height = 4)
p
```

Which trend line in the above plot are statistically significant?
```{r}
df= phenotype_rank_all_by_year %>% left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year')
trendline_lm_test <- df %>% 
  filter(distancetoroot == 1) %>% 
  filter(lab_year > 2000) %>% 
  mutate(fraction = n_patient / n_tested) %>%
  select(termid, lab_year, label, fraction) %>% 
  group_by(termid, label) %>% 
  nest() %>% 
  mutate(lm_model = map(data, function(d) lm(fraction ~ lab_year, data = d))) %>%
  mutate(lm_coeff = map(lm_model, broom::tidy)) %>%
  select(-data, -lm_model) %>% 
  unnest(lm_coeff) %>% 
  filter(term == 'lab_year') %>% 
  mutate(p.value.bonferroni = p.value * 10)

symnum(trendline_lm_test$p.value.bonferroni, cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, Inf), symbols = c("***", "**", "*", ".", " "))

trendline_lm_test_formatted <- trendline_lm_test %>% select(termid, label, estimate, p.value, p.value.bonferroni) %>% 
  arrange(p.value.bonferroni) %>%
  rename(beta = estimate) %>% 
  mutate(significance = symnum(p.value.bonferroni, cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, Inf), symbols = c("***", "**", "*", ".", " ")) ) %>% 
  mutate(across(.cols = function(x) is.double(x), function(x) scales::scientific(x, digits = 3)))

write.csv(trendline_lm_test_formatted, file = glue('{CACHE_DIR}/table_abnormal_phenotypes_by_year_level_1_normalized_trendline_lm_model.csv'), row.names=FALSE)

trendline_lm_test_formatted
```

@@

tested_phenotype_rank_direct <- get_tested_phenotype_rank_direct(force_rerun = FORCE_RERUN)
tested_phenotype_rank_all <- get_tested_phenotype_rank_all(force_rerun = FORCE_RERUN)
```

@@

tested_phenotype_rank_all_by_year <- get_tested_phenotype_rank_all_by_year(force_rerun = FORCE_RERUN)
```

```{r}
hpo_level_1_terms <- tested_phenotype_rank_all_by_year %>% filter(distancetoroot == 1) %>% select(termid, label) %>% distinct()
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=tested_phenotype_rank_all_by_year, normalize = FALSE)
ggsave(filename = glue('{CACHE_DIR}/plot_tested_phenotypes_by_year_level_1.pdf'), plot = p, width = 8, height = 4)
p
```
```{r}
p <- plot_phenotypes_of_interest_by_year(terms_of_interest = hpo_level_1_terms$termid, df=tested_phenotype_rank_all_by_year %>% left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'), normalize = TRUE)
ggsave(filename = glue('{CACHE_DIR}/plot_tested_phenotypes_by_year_level_1_normalized.pdf'), plot = p, width = 8, height = 4)
p
```

```{r}
df= tested_phenotype_rank_all_by_year %>% left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year')
trendline_lm_test <- df %>% 
  filter(distancetoroot == 1) %>% 
  filter(lab_year > 2000) %>% 
  mutate(fraction = n_patient / n_tested) %>%
  select(termid, lab_year, label, fraction) %>% 
  group_by(termid, label) %>% 
  nest() %>% 
  mutate(lm_model = map(data, function(d) lm(fraction ~ lab_year, data = d))) %>%
  mutate(lm_coeff = map(lm_model, broom::tidy)) %>%
  select(-data, -lm_model) %>% 
  unnest(lm_coeff) %>% 
  filter(term == 'lab_year') %>% 
  mutate(p.value.bonferroni = p.value * 11)

trendline_lm_test_formatted <- trendline_lm_test %>% select(termid, label, estimate, p.value, p.value.bonferroni) %>% 
  arrange(p.value.bonferroni) %>%
  rename(beta = estimate) %>% 
  mutate(significance = symnum(p.value.bonferroni, cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, Inf), symbols = c("***", "**", "*", ".", " ")) ) %>% 
  mutate(across(.cols = function(x) is.double(x), function(x) scales::scientific(x, digits = 3)))

write.csv(trendline_lm_test_formatted, file = glue('{CACHE_DIR}/table_tested_phenotypes_by_year_level_1_normalized_trendline_lm_model.csv'), row.names=FALSE)

trendline_lm_test_formatted
```

```{r}
children_abnormal_cellular_physiology <- c('HP:0003220', 'HP:0011018', 'HP:0025463', 'HP:0011019', 'HP:0003254', 'HP:4000056', 'HP:0011133', 'HP:0004371', 'HP:0031377', 'HP:0031409', 'HP:0012103', 'HP:0032576', 'HP:0003204', 'HP:0004356', 'HP:0032571', 'HP:0002916', 'HP:0003224', 'HP:0003575', 'HP:0003358')
plot_phenotypes_of_interest_by_year(terms_of_interest = children_abnormal_cellular_physiology, df=tested_phenotype_rank_all_by_year %>% left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'))
```

Again, the above plot shows that it is driven by one HP:0031409 Abnormal lymphocyte physiology. 
```{r}
children_of_interest <- c('HP:0011840', 'HP:0030886', 'HP:0012177', 'HP:0005372', 'HP:0031378')
plot_phenotypes_of_interest_by_year(terms_of_interest = children_of_interest, df=tested_phenotype_rank_all_by_year %>% left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'))
```
```{r}
children_of_interest <- c('HP:0002847', 'HP:0002959', 'HP:0005384', 'HP:0041076', 'HP:0010701')
plot_phenotypes_of_interest_by_year(terms_of_interest = children_of_interest, df=tested_phenotype_rank_all_by_year %>% left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'))
```

```{r}
children_of_interest <- c('HP:0010702', 'HP:0032336', 'HP:0410241', 'HP:0410240', 'HP:0410243', 'HP:0410242', 'HP:0410244', 'HP:0004313')
plot_phenotypes_of_interest_by_year(terms_of_interest = children_of_interest, df=tested_phenotype_rank_all_by_year %>% left_join(tested_patient_count_by_year %>% rename(n_tested = n_patient), by = 'lab_year'))
```

tested_phenotype_spike_by_loinc_year <- get_tested_phenotype_spike_by_loinc_year(force_rerun = FORCE_RERUN)
tested_phenotype_spike_by_localcode_year <- get_tested_phenotype_spike_by_localcode_year(force_rerun = FORCE_RERUN)
```

### Analyze racial differences

#### racial differences of tested phenotypes

The section analyzed whether there are racial differences in tested phenotypes. The problem is that we saw the vast majority of terms have differences. This is probably just a large number effect.

@@

tested_phenotype_rank_direct_by_race <- get_tested_phenotype_rank_direct_by_race(force_rerun = FORCE_RERUN)
tested_phenotype_rank_all_by_race <- get_tested_phenotype_rank_all_by_race(force_rerun = FORCE_RERUN)
```

For each directly measured phenotype, we can determine whether race and the tests are correlated by some form of Chi-squared test. The current problem is that the most phenotype terms are statistically significant. 
@TODO we should look at phenotypes at each year. 
```{r}
countByRace <- patient_race_sex_distribution %>% 
  group_by(race) %>% 
  summarise(dbtotal = sum(n))

phenotype_race_chisq_test <- function(df) {
  broom::tidy(chisq.test(df$observed, p = df$dbtotal/sum(df$dbtotal)))
}

phenotype_race_prop_test <- function(df){
  broom::tidy(prop.test(df$observed, p = df$observed/sum(df$dbtotal)))
}

tested_phenotype_rank_direct_by_race %>% 
  select(termid, label, race, n_patient) %>% 
  rename(observed = n_patient) %>% 
  group_by(termid, label) %>% 
  nest() %>% 
  mutate(data = map(data, function(d) d %>% 
                      right_join(countByRace, by = 'race') %>%
                      replace_na(list(termid = first(.$termid), label = first(.$label), observed = 0)))) %>% 
  mutate(chisq = map(data, phenotype_race_chisq_test)) %>% 
  select(-data) %>% 
  unnest(chisq) %>% 
  arrange(-p.value)
```

```{r}
tested_phenotype_rank_all_by_race %>% filter(distancetoroot == 1) %>% 
  select(termid, label, race, n_patient) %>% 
  rename(observed = n_patient) %>% 
  group_by(termid, label) %>% 
  nest() %>% 
  mutate(data = map(data, function(d) d %>% 
                      right_join(countByRace, by = 'race') %>%
                      replace_na(list(termid = first(.$termid), label = first(.$label), observed = 0)))) %>% 
  mutate(chisq = map(data, phenotype_race_chisq_test)) %>% 
  select(-data) %>% 
  unnest(chisq) %>% 
  arrange(-p.value)
```

#### racial differences of observed abnormal phenotypes by races
An improved version of racial analysis: 
Question: for each race, is it more likely to have a certain abnormal phenotype than the rest of the population?

To do this, we will run Chisq test but on annual basis. 
```{r}
tested_patient_count_by_year_race <- tested_patient_count_by_year_race_sex %>% 
  group_by(lab_year, race) %>% 
  summarise(dbtotal = sum(n_patient), .groups = 'drop')

tested_patient_count_by_year_race %>% filter(lab_year == 2019)
```

```{r}
RACE_OF_INTEREST <- 'Black or African American'
df <- phenotype_rank_all_by_year_race_sex %>% 
  group_by(termid, label, lab_year, race) %>% 
  summarise(observed = sum(n_patient), .groups = 'drop') %>% 
  right_join(tested_patient_count_by_year_race, by = c('lab_year', 'race')) %>% 
  filter(lab_year == 2019) %>% 
  ##filter(termid == 'HP:0003351')
  filter(termid == 'HP:0000079')

cm <- df %>%
  mutate(roi = if_else(race == RACE_OF_INTEREST, 'isROI', 'notROI')) %>% 
  group_by(roi) %>% 
  summarise(observed = sum(observed), dbtotal = sum(dbtotal)) %>% 
  ungroup() %>%
  mutate(not_observed = dbtotal - observed) %>% 
  select(-dbtotal) %>%
  column_to_rownames('roi') %>% 
  t() %>% 
  as.matrix()

broom::tidy(fisher.test(cm))

## write a function to test the statistical difference for each race
racial_abnormality_statistical_test <- function(df){
  if (nrow(df) <= 1) {
    return (NULL)
  }
  fisher_tests_races <- list()
  for (RACE_OF_INTEREST in df$race){
    cm <- df %>%
        mutate(roi = if_else(race == RACE_OF_INTEREST, 'isROI', 'notROI')) %>% 
        group_by(roi) %>% 
        summarise(observed = sum(observed), dbtotal = sum(dbtotal)) %>% 
        ungroup() %>%
        mutate(not_observed = dbtotal - observed) %>% 
        select(-dbtotal) %>%
        column_to_rownames('roi') %>% 
        t() %>% 
        as.matrix()
    if (length(cm) == 4){
       fisher_test_coeff <- broom::tidy(fisher.test(cm))
    } else {
       fisher_test_coeff <- data.frame(estimate = numeric(), p.value = numeric(), conf.low = numeric(), conf.high = numeric(), method = '', alternative = '')
    }
    fisher_test_coeff <- fisher_test_coeff %>% mutate(race = RACE_OF_INTEREST) %>% 
      select(race, everything())
    fisher_tests_races[[length(fisher_tests_races) + 1]] <- fisher_test_coeff
  }
  fisher_test_coeffs <- bind_rows(fisher_tests_races)
  ##return (df %>% left_join(fisher_test_coeffs, by = 'race'))
  return (fisher_test_coeffs)
}

racial_abnormality_statistical_test(df)

library(furrr)

plan(multisession, workers = 8)

racial_abnormality_fisher <- phenotype_rank_all_by_year_race_sex %>% 
  group_by(termid, label, lab_year, race) %>% 
  summarise(observed = sum(n_patient), .groups = 'drop') %>% 
  right_join(tested_patient_count_by_year_race, by = c('lab_year', 'race')) %>% 
  #filter(lab_year == 2019) %>% 
  #filter(termid %in% c('HP:0003351', 'HP:0000079')) %>% 
  group_by(lab_year, termid, label) %>% 
  nest() %>% 
  ungroup() %>% 
  mutate(fisher_coeff = future_map(data, racial_abnormality_statistical_test)) %>% 
  select(-data) %>% 
  unnest(fisher_coeff)

racial_abnormality_fisher %>% nrow()

write.csv(racial_abnormality_fisher, file = glue('{CACHE_DIR}/racial_abnormality_fisher.csv'), row.names = FALSE)

racial_abnormality_fisher %>% filter(between(lab_year, 2000, 2019)) %>% 
  filter(race == 'Black or African American') %>% 
  filter(termid %in% hpo_level_1_terms$termid) %>% 
  {
    ggplot(., aes(x = lab_year, y = estimate, group = termid, color = termid)) + 
    geom_point() +
    geom_line() +
    scale_color_discrete(breaks = .$termid, labels = str_c(.$termid, .$label, sep = " ")) +
    xlab('Year') +
    ylab('odds ratio') +
    theme_bw() +
    theme(panel.grid = element_blank(),
        axis.title = element_text(size = 8), axis.text = element_text(size = 8), 
        legend.text = element_text(size = 8), legend.title = element_text(size = 10))
